The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-14 paper/model_2.tex
merge model 2 figs; add aastex cmds

\begin{figure}[!t]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_2.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        Model 
        \#2.
        This model has fixed planets and primaries, but varying secondaries.
    }
    \label{fig:errcases_model_2_linear}
\end{figure}
\begin{figure}[!h]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_2.pdf}
    \caption{
        Same as Fig.~\ref{fig:errcases_model_2_linear}, but with logarithmic 
        $y$-axis, and different $x$ scale.
    }
    \label{fig:errcases_model_2_log}
\end{figure}

@@

\paragraph{Numerical results for Model \#2}
We first validate our model by ensuring it produces the analytically-predicted 
results for Model \#1, and the limiting case of Model \#2 described above.
Following validation, assuming ${\rm BF}=0.44$, $\alpha=3.5$, 
$\beta=\gamma=0$, and taking $Z_0=Z_1=Z_2=0.5$, we compute the true and 
apparent occurrence rates over bins in planet radius.
The results are shown in Figs.~\ref{fig:errcases_model_2_linear} 
and~\ref{fig:errcases_model_2_log}.
Evidently, dilution produces a spectrum of apparent planetary radii. This 
leads to overestimated rates everywhere except where there 
are actually planets, where the rate is underestimated by a factor of two.

>>>>

\begin{figure}
\centering
\epsscale{1.3}
\plottwo{figures/errcases_rate_density_vs_radius_model_2.pdf}{figures/errcases_rate_density_vs_radius_logs_model_2.pdf}
\caption{
Inferred planet occurrence rates as a function of planet radius in Model \#2 
({\it top:} linear, {\it bottom:} logarithmic).
This model has fixed planets and primaries, and varying secondary masses, 
radii, and luminosities.
The latter three lines are described in Fig.~\ref{fig:errcases_model_1}.
\label{fig:errcases_model_2}}
\end{figure}

\begin{comment}
\begin{figure}[!t]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_2.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        Model 
        \#2.
        This model has fixed planets and primaries, but varying secondaries.
    }
    \label{fig:errcases_model_2_linear}
\end{figure}
\begin{figure}[!h]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_2.pdf}
    \caption{
        Same as Fig.~\ref{fig:errcases_model_2_linear}, but with logarithmic 
        $y$-axis, and different $x$ scale.
    }
    \label{fig:errcases_model_2_log}
\end{figure}
\end{comment}

@@

\paragraph{Numerical results for Model \#2}
We first validate our model by ensuring it produces the analytically-predicted 
results for Model \#1, and the limiting case of Model \#2 described above.
Following validation, assuming ${\rm BF}=0.44$, $\alpha=3.5$, 
$\beta=\gamma=0$, and taking $Z_0=Z_1=Z_2=0.5$, we compute the true and 
apparent occurrence rates over bins in planet radius.
The results are shown in Fig.~\ref{fig:errcases_model_2}.
Evidently, dilution produces a spectrum of apparent planetary radii. This 
leads to overestimated rates everywhere except where there 
are actually planets, where the rate is underestimated by a factor of two.
